Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-02-13 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf

Expanding on the problem formulation in the introduction, we want to approximate well the integral or expectation, $\mu$, by the sample mean, $\hat{\mu}$:
\begin{gather}
\label{eq:cubSummary}
	\mu : = \int_\calT g(\bst) \, \lambda(\bst) \, \D \bst  = \bbE[f(\bsX)] = \int_{[0,1]^d} f(\bsx)  \, \D \bsx \approx \frac 1n \sum_{i=0}^{n-1} f(\bsx_i) =: \hat{\mu}_n, \\
 \label{CDHS_eq:error_tol}
 \abs{\mu - \hat{\mu}_n} \le \varepsilon.
\end{gather}
Progressing from the original problem to a satisfactory solution requires several software components.  Great QMC software environment allows different implementations of these components to be interchanged.

@@

\subsection{Integrands and Variable Transformations} The original integral or expectation arising from the application is defined in terms of the integrand, $g$, and the non-negative weight, $\lambda$.  For example,
\begin{itemize}
	\item $g$ is the discounted payoff of a financial derivative and $\lambda$ be the probability density function (PDF) for a discretized Brownian motion \cite{Gla03},

	\item  $g$ is the velocity of a fluid at a point in rock with a random porosity field whose discretized PDF is $\lambda$, or

	\item $g\lambda$ is the unnormalized Bayesian posterior density multiplied by parameter of interest.
\end{itemize},
If $\lambda$ is a probability density function for a random variable $\bsT$, then $\mu = \EE[g(\bsT)]$.

To put $\mu$ into the form that is directly accessible to QMC methods requires a \emph{variable transformation}, $\bsPsi$, such that
\begin{equation*}
    \Psi((0,1)^d) = \calT, \qquad f(x) = g(\bsPsi(\bsx)) \lambda(\bsPsi(\bsx)) \abs{\frac{\partial \bsPsi}{\partial{\bsx}}}.
\end{equation*}
Such a transformation is typically non-unique, and the choice of a good one is equivalent to importance sampling.

>>>>

Expanding on the problem formulation in the introduction, we want to approximate well the integral or expectation, $\mu$, by the sample mean, $\hat{\mu}$:
\begin{gather}
\label{eq:cubSummary}
	\mu : = \int_\calT g(\bst) \, \lambda(\bst) \, \D \bst  = \bbE[f(\bsX)] = \int_{[0,1]^d} f(\bsx)  \, \D \bsx \approx \frac 1n \sum_{i=0}^{n-1} f(\bsx_i) =: \hat{\mu}_n, \\
 \label{CDHS_eq:error_tol}
 \abs{\mu - \hat{\mu}_n} \le \varepsilon.
\end{gather}
Progressing from the original problem to a satisfactory solution requires several software components, which we describe in the subsections below.  Great QMC software environments allows different implementations of these components to be interchanged.

@@

For the comprehensive software environments, such as NAG, MATLAB, R, SciPy, and TensorFlow, including the LD sequence generators allow users to a ????

\subsection{Integrands and Variable Transformations} The original integral or expectation arising from the application is defined in terms of the integrand, $g$, and the non-negative weight, $\lambda$.  For example,
\begin{itemize}
	\item $g$ is the discounted payoff of a financial derivative and $\lambda$ is the probability density function (PDF) for a discretized Brownian motion \cite{Gla03},

	\item  $g$ is the velocity of a fluid at a point in rock with a random porosity field whose discretized PDF is $\lambda$ \cite{}, or

	\item $g\lambda$ is the unnormalized Bayesian posterior density multiplied by parameter of interest.
\end{itemize}

To put $\mu$ into the form that is directly accessible to QMC methods requires a \emph{variable transformation}, $\bsPsi$, such that
\begin{equation*}
    \Psi((0,1)^d) = \calT, \qquad f(\bsx) = g(\bsPsi(\bsx)) \lambda(\bsPsi(\bsx)) \abs{\frac{\partial \bsPsi}{\partial\bsx}}.
\end{equation*}
Such a transformation is typically non-unique, and the choice of a good one is equivalent to importance sampling.  If $\lambda$ is a PDF for a random variable $\bsT$, then $\mu = \EE[g(\bsT)]$.  Moreover, one might choose $\bsPsi$ such that $\bsT = \bsPsi(\bsX)$, in which case $\lambda(\bsPsi(\bsx)) \abs{\partial \bsPsi/\partial\bsx} = 1$ and $f(\bsx) = g(\bsPsi(\bsx))$.
